GOV 1006: Milestone 6

### 2020-04-18 milestone6.Rmd
still can't figure out the alignment of my stargazer tables

---
title: "GOV 1006: Milestone 6"
subtitle: "Paper Replication"
author: "Pieter Quinton"
date: "4/3/2020"
output: 
  bookdown::pdf_document2:
    keep_tex: true
bibliography: milestone5_bib.bib
---

@@

library(stargazer)
library(plyr)
library(plm)
library(wfe)
library(tidyverse)
```

@@

>>>>

---
title: "GOV 1006: Milestone 6"
subtitle: "Paper Replication"
author: "Pieter Quinton"
date: "4/3/2020"
output: 
  bookdown::pdf_document2:
    keep_tex: true
document_class: article
bibliography: milestone5_bib.bib
---

@@

library(rsconnect)
library(stargazer)
library(plyr)
library(plm)
library(wfe)
library(tidyverse)
```

@@

```{r extension}

liss_2.0 <- liss %>%
  group_by(unit) %>%
  summarize(total_unemployment = sum(unemployed))

liss_3.0 <- liss %>%
  filter(time == 2014) %>%
  inner_join(liss_2.0, by = "unit")

modelExtension_1 <- lm(trust_in_government ~ unemployed + age + education + member, data = liss_3.0)

liss <- liss %>%
  group_by(unit) %>%
  arrange(time) %>%
  mutate(lagged_unemployed = lag(unemployed)) %>%
  ungroup(unit)

shp_2.0 <- shp %>%
  group_by(unit) %>%
  summarize(total_unemployment = sum(unemployed))

shp <- shp %>%
  group_by(unit) %>%
  arrange(time) %>%
  mutate(lagged_unemployed = lag(unemployed)) %>%
  ungroup(unit)

```{r tableExtension, results = 'asis'}

shp.fit.fe.tig.ext <- plm(trust_in_government ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.ls.ext <- plm(life_satisfaction ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.control.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.control.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.control.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.tig.ext <- plm(trust_in_government ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.ls.ext <- plm(life_satisfaction ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.control.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.control.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.control.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

stargazer(shp.fit.fe.tig.ext, shp.fit.fe.control.tig.ext, shp.fit.fe.swd.ext, shp.fit.fe.control.swd.ext, shp.fit.fe.ls.ext, shp.fit.fe.control.ls.ext, liss.fit.fe.tig.ext, liss.fit.fe.control.tig.ext, liss.fit.fe.swd.ext, liss.fit.fe.control.swd.ext, liss.fit.fe.ls.ext, liss.fit.fe.control.ls.ext,
          omit.stat=c("LL","ser","f","adj.rsq"),
          header = FALSE,
          font.size = "tiny",
          digits = 2,
          label = "table-5",
          column.sep.width = "-7.5pt",
          title = "SHP Switzerland and LISS Netherlands: fixed effects models with lagged unemployment",
          column.labels = c("(M13)", "(M14)", "(M15)", "(M16)", "(M17)", "(M18)", "(M19)", "(M20)", "(M21)", "(M22)", "(M23)", "(M24)"),
          covariate.labels = c("Unemployed", "Lagged Unemployed", "Unemployed:Lagged Unemployed", "Age", "Education", "Member"),
          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
          model.names = FALSE,
          model.numbers = FALSE
          )
```
